### 2017-10-18 pkg/model4you/inst/JORS/man_model4you.Rnw
small changes of text
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1661 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 414146413ce2ec20a2a697e59276c2b39360e41b

\section*{Implementation and architecture}
The R package \emph{model4you} is focussed on ease of use and interpretability.
Users can take a simple model that they know and understand as basis and simply
plug it into \Sexpr{'pmtree()'} or \Sexpr{'pmforest()'} depending on whether
they want subgroup wise or personalised models. The basis for these
functionalities is provided by the \emph{partykit} package which is a widely
used R package for trees and forests. The \emph{model4you} package provides
wrappers for the well implemented and tested functions
\Sexpr{'partykit::ctree()'} and \Sexpr{'partykit::cforest()'} and extends the
functionalities where needed to improve usability and interpretability.

The \emph{partykit} package provides the basis for functionalities in other
packages namely \emph{glmertree}, \emph{psychotree}, \emph{betareg} (all on
CRAN), \emph{trtf}, \emph{disttree}, \emph{lagsarlmtree} and \emph{palmtree}
(all available on R-Forge with a plan to move them to CRAN).

>>>>

\section*{Implementation and architecture}
The R package \emph{model4you} is focussed on ease of use and interpretability.
Users can take a simple model that they know and understand as basis and simply
plug it into \Sexpr{'pmtree()'} or \Sexpr{'pmforest()'} depending on whether
they want subgroup wise or personalised models. The basis for these
functionalities is provided by the \emph{partykit} package which is a widely
used R package for trees and forests. The \emph{model4you} package provides
wrappers for the well implemented and tested functions
\Sexpr{'partykit::ctree()'} and \Sexpr{'partykit::cforest()'} and extends the
functionalities to allow for the computation of personalised models and to 
improve usability and interpretability.

The \emph{partykit} package provides the basis for functionalities in other
packages namely \emph{glmertree}, \emph{psychotree}, \emph{betareg} (all on
CRAN), \emph{trtf}, \emph{disttree}, \emph{lagsarlmtree} and \emph{palmtree}
(all available on R-Forge, publishing on CRAN planned).
